Housing Market Institutions Drive Race and Ethnicity Differences in Energy Consumption

### 2015-03-28 ConferencePaper/DraftEdwardsWoods.tex
27mar
mar27

\begin{itemize}
  \item Description on RECS data size number of observations sampling method etc.
  \item Scope of data  
  \item Weighting to account for stratified sampling
  \item We need more tables and graphics here.
\end{itemize}

% latex table generated in R 3.0.1 by xtable 1.7-4 package
% Thu Mar 26 16:51:35 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrr}
  \hline
 & Mobile & SFDetached & SFAttached & SmApartment & LgApartment \\ 
  \hline
FALSEWt & 371 & 5694 & 544 & 430 & 951 \\ 
  FALSEAfAm &  24 & 754 & 121 & 174 & 382 \\ 
  FALSEAsian &   1 & 231 &  48 &  52 & 113 \\ 
  FALSEMulti &   6 &  87 &  14 &  12 &  27 \\ 
  FALSENativeAm &   7 &  35 &   9 &   7 &  15 \\ 
  FALSEOther &   2 &  59 &   8 &  13 &  29 \\ 
  FALSEPacific &   1 &  22 &   1 &   2 &  10 \\ 
  TRUEAfAm &   3 &   8 &  10 &   5 &   8 \\ 
  TRUEAsian &   0 &   5 &   0 &   0 &   1 \\ 
  TRUEMulti &   1 &  10 &   2 &   4 &   4 \\ 
  TRUENativeAm &   2 &  17 &   3 &   6 &   9 \\ 
  TRUEOther &   6 &  41 &  12 &  16 &  24 \\ 
  TRUEPacific &   0 &   2 &   1 &   1 &   0 \\ 
  TRUEWt &  97 & 730 & 105 & 184 & 332 \\ 
   \hline
\end{tabular}
\caption{Count of Observations by Race and Structure Type} 
\label{tab:RaceVStruct}
\end{table}
% latex table generated in R 3.0.1 by xtable 1.7-4 package
% Thu Mar 26 16:51:35 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrr}
  \hline
 & Mobile & SFDetached & SFAttached & SmApartment & LgApartment \\ 
  \hline
NE &  47 & 1173 & 218 & 326 & 470 \\ 
  MidWest &  92 & 2080 & 162 & 145 & 323 \\ 
  South & 245 & 2685 & 257 & 226 & 603 \\ 
  West & 137 & 1757 & 241 & 209 & 509 \\ 
   \hline
\end{tabular}
\caption{Count of Observations by Region and Structure Type} 
\label{tab:RegionVStruct}
\end{table}
\begin{figure}
\begin{center}
\caption{Annual kWh by Rent/Own and Race}
\label{fig:kWhbyOwnRace}
\includegraphics{DraftEdwardsWoods-005}
\end{center}
\end{figure}

@@

% latex table generated in R 3.0.1 by xtable 1.7-4 package
% Thu Mar 26 16:51:53 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrr}
  \hline
 & FALSE & TRUE \\ 
  \hline
FALSEWt & 7606 & 384 \\ 
  FALSEAfAm & 1367 &  88 \\ 
  FALSEAsian & 424 &  21 \\ 
  FALSEMulti & 133 &  13 \\ 
  FALSENativeAm &  68 &   5 \\ 
  FALSEOther & 102 &   9 \\ 
  FALSEPacific &  30 &   6 \\ 
  TRUEAfAm &  31 &   3 \\ 
  TRUEAsian &   4 &   2 \\ 
  TRUEMulti &  19 &   2 \\ 
  TRUENativeAm &  36 &   1 \\ 
  TRUEOther &  88 &  11 \\ 
  TRUEPacific &   4 &   0 \\ 
  TRUEWt & 1330 & 118 \\ 
   \hline
\end{tabular}
\caption{EnergyStar Wall AC by Race and Ethnicity} 
\label{tab:EnergyStarWall}
\end{table}

% latex table generated in R 3.0.1 by xtable 1.7-4 package
% Thu Mar 26 16:51:53 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrr}
  \hline
 & Rural & Urban \\ 
  \hline
FALSEWt & 1937 & 6053 \\ 
  FALSEAfAm & 192 & 1263 \\ 
  FALSEAsian &  14 & 431 \\ 
  FALSEMulti &  28 & 118 \\ 
  FALSENativeAm &  25 &  48 \\ 
  FALSEOther &  12 &  99 \\ 
  FALSEPacific &   4 &  32 \\ 
  TRUEAfAm &   6 &  28 \\ 
  TRUEAsian &   0 &   6 \\ 
  TRUEMulti &   1 &  20 \\ 
  TRUENativeAm &   3 &  34 \\ 
  TRUEOther &   5 &  94 \\ 
  TRUEPacific &   2 &   2 \\ 
  TRUEWt & 137 & 1311 \\ 
   \hline
\end{tabular}
\caption{Race by Urban/Rural} 
\label{tab:UrbRural}
\end{table}

% latex table generated in R 3.0.1 by xtable 1.7-4 package
% Thu Mar 26 16:51:53 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrrrrr}
  \hline
 & NG & LPG & Oil & Kerosene & Elec & Wood & Solar & Other \\ 
  \hline
FALSEWt & 4077 & 315 & 361 &   3 & 3190 &  11 &  12 &   7 \\ 
  FALSEAfAm & 755 &  17 &  35 &   0 & 640 &   0 &   2 &   0 \\ 
  FALSEAsian & 312 &   7 &  12 &   0 & 109 &   0 &   0 &   2 \\ 
  FALSEMulti &  85 &   5 &   3 &   0 &  53 &   0 &   0 &   0 \\ 
  FALSENativeAm &  34 &   2 &   1 &   0 &  36 &   0 &   0 &   0 \\ 
  FALSEOther &  57 &   3 &   6 &   0 &  44 &   0 &   0 &   0 \\ 
  FALSEPacific &  15 &   0 &   2 &   0 &  17 &   0 &   2 &   0 \\ 
  TRUEAfAm &  20 &   0 &   1 &   0 &  13 &   0 &   0 &   0 \\ 
  TRUEAsian &   5 &   0 &   0 &   0 &   1 &   0 &   0 &   0 \\ 
  TRUEMulti &  12 &   0 &   1 &   0 &   8 &   0 &   0 &   0 \\ 
  TRUENativeAm &  29 &   0 &   0 &   0 &   8 &   0 &   0 &   0 \\ 
  TRUEOther &  62 &   1 &   5 &   0 &  30 &   0 &   0 &   0 \\ 
  TRUEPacific &   1 &   1 &   0 &   0 &   2 &   0 &   0 &   0 \\ 
  TRUEWt & 830 &  33 &  26 &   0 & 552 &   0 &   1 &   0 \\ 
   \hline
\end{tabular}
\caption{Water Service by Race and Ethnicity} 
\label{tab:Water}
\end{table}
% latex table generated in R 3.0.1 by xtable 1.7-4 package
% Thu Mar 26 16:51:53 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrrrrrr}
  \hline
 & NG & LPG & Oil & Kerosene & Elec & Wood & Solar & District & Other \\ 
  \hline
FALSEWt & 3987 & 400 & 642 &  40 & 2515 & 245 &   1 &  11 &  19 \\ 
  FALSEAfAm & 674 &  29 &  60 &   6 & 640 &  10 &   0 &   5 &   0 \\ 
  FALSEAsian & 249 &   1 &  21 &   0 & 122 &   1 &   0 &   2 &   0 \\ 
  FALSEMulti &  80 &   6 &   7 &   0 &  41 &   7 &   0 &   0 &   1 \\ 
  FALSENativeAm &  34 &   3 &   1 &   0 &  33 &   2 &   0 &   0 &   0 \\ 
  FALSEOther &  59 &   1 &   9 &   0 &  36 &   3 &   0 &   0 &   0 \\ 
  FALSEPacific &  16 &   0 &   2 &   0 &   5 &   1 &   0 &   0 &   0 \\ 
  TRUEAfAm &  21 &   0 &   1 &   1 &   9 &   0 &   0 &   0 &   0 \\ 
  TRUEAsian &   4 &   0 &   0 &   0 &   1 &   0 &   0 &   0 &   0 \\ 
  TRUEMulti &  11 &   0 &   4 &   0 &   4 &   1 &   0 &   0 &   0 \\ 
  TRUENativeAm &  26 &   1 &   2 &   0 &   7 &   0 &   0 &   0 &   0 \\ 
  TRUEOther &  53 &   0 &   8 &   1 &  32 &   0 &   0 &   2 &   0 \\ 
  TRUEPacific &   1 &   0 &   0 &   0 &   2 &   0 &   0 &   0 &   0 \\ 
  TRUEWt & 604 &  25 &  51 &   2 & 540 &  18 &   0 &   3 &   1 \\ 
   \hline
\end{tabular}
\caption{Heating Fuel by Race and Ethnicity} 
\label{tab:HeatFuel}
\end{table}
% latex table generated in R 3.0.1 by xtable 1.7-4 package
% Thu Mar 26 16:51:53 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrr}
  \hline
 & VColdCold & HotDryMixedDry & HotHumid & MixedHumid & Marine \\ 
  \hline
FALSEWt & 3118 & 850 & 1216 & 2382 & 424 \\ 
  FALSEAfAm & 299 & 131 & 383 & 611 &  31 \\ 
  FALSEAsian &  95 & 128 &  60 &  77 &  85 \\ 
  FALSEMulti &  51 &  27 &  13 &  40 &  15 \\ 
  FALSENativeAm &  23 &  10 &   7 &  28 &   5 \\ 
  FALSEOther &  29 &  16 &  24 &  37 &   5 \\ 
  FALSEPacific &   4 &   6 &  13 &   4 &   9 \\ 
  TRUEAfAm &  16 &   5 &   4 &   9 &   0 \\ 
  TRUEAsian &   2 &   2 &   1 &   0 &   1 \\ 
  TRUEMulti &  12 &   6 &   1 &   0 &   2 \\ 
  TRUENativeAm &   9 &  14 &   1 &   8 &   5 \\ 
  TRUEOther &  35 &  19 &  10 &  28 &   7 \\ 
  TRUEPacific &   2 &   0 &   2 &   0 &   0 \\ 
  TRUEWt & 237 & 481 & 406 & 237 &  87 \\ 
   \hline
\end{tabular}
\caption{Climate by Race and Ethnicity} 
\label{tab:Climate}
\end{table}
\begin{figure}
\begin{center}
\caption{Age of Structure by Rent/Own and Race/Ethnicity}
\label{fig:AgebyOwnRace}
\includegraphics{DraftEdwardsWoods-013}
\end{center}
\end{figure}

@@

% latex table generated in R 3.0.1 by xtable 1.7-4 package
% Thu Mar 26 16:51:57 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrrrr}
  \hline
 & Never & ThreeDay & TwoDay & OneDay & FewWeek & OneWeek & LessWeek \\ 
  \hline
FALSEWt &  67 & 452 & 1814 & 3303 & 1825 & 254 & 275 \\ 
  FALSEAfAm &  11 & 156 & 351 & 341 & 448 &  80 &  68 \\ 
  FALSEAsian &   4 &  63 & 111 & 148 &  91 &  13 &  15 \\ 
  FALSEMulti &   2 &  14 &  45 &  40 &  36 &   7 &   2 \\ 
  FALSENativeAm &   0 &   7 &  22 &  27 &  11 &   3 &   3 \\ 
  FALSEOther &   2 &  10 &  25 &  21 &  43 &   3 &   7 \\ 
  FALSEPacific &   0 &   3 &   9 &  10 &  11 &   0 &   3 \\ 
  TRUEAfAm &   1 &   4 &   7 &  13 &   9 &   0 &   0 \\ 
  TRUEAsian &   0 &   0 &   1 &   3 &   2 &   0 &   0 \\ 
  TRUEMulti &   0 &   2 &   1 &  11 &   5 &   2 &   0 \\ 
  TRUENativeAm &   0 &   3 &  12 &  15 &   4 &   2 &   1 \\ 
  TRUEOther &   0 &  20 &  28 &  31 &  14 &   3 &   3 \\ 
  TRUEPacific &   0 &   3 &   0 &   1 &   0 &   0 &   0 \\ 
  TRUEWt &  22 & 208 & 453 & 435 & 226 &  42 &  62 \\ 
   \hline
\end{tabular}
\caption{Weekly Meals Cooked by Race and Ethnicity} 
\label{tab:Cooking}
\end{table}
\begin{figure}
\begin{center}
\caption{Daytime Temp and Race/Ethnicity (Winter)}
\label{fig:TempHomeRace}
\includegraphics{DraftEdwardsWoods-015}
\end{center}
\end{figure}

@@

% latex table generated in R 3.0.1 by xtable 1.7-4 package
% Thu Mar 26 16:54:09 2015

>>>>

RECS data set is the 2009 publication.  12083 observations are included in the data, of which 11395 are included in the struture-tenure model.
\begin{itemize}
  \item Description on RECS data size number of observations sampling method etc.
  \item Scope of data  
  \item Weighting to account for stratified sampling
  \item We need more tables and graphics here.
\end{itemize}

Variable and Data Description:

The RASS data set includes 25721 observations from households.  Of these observations, many respondents to the survey left questions blank and thus those respondent’s information is omitted from the analysis.  Nonetheless, 20,303 observations are included in applying the model.   Observations are taken from households across the state of California and the initial phase of the RASS consisted of a mail out survey that in total had a 20% response rate (RASS Methodology 21) across stratums.  While the data set includes 564 variables only a small portion of those are used to construct our model.
  First, our dependent variable is constructed by combing dwelling type (dwltype) and the binary response variable Ownrent.  Dwltype includes six categories as follows: single family detached house, townhouse (including duplex, or row house), small apartment complex, large apartment complex, mobile home, and other.  For our purposes the category of other was dropped from the analysis.  As well mobile homes are noted with having considerably fewer observations than other categories.  Thus, we end with ten categories, the previous five dwelling types combined with whether the household is renting/leasing or buying/own the home.
	Next, our independent variables are as follows: income, resident ages, education, and ethnicity.  Income is categorized into twelve separate options ranging from less than ten thousand to over one hundred and fifty thousand dollars total annually. Resident characteristics describe the number of individuals in the household including children, adults, and seniors.  Education is broken into six categories describing highest education level completed by the head of the household: elementary, some high school, high school. Some college/trade/vocational school, college graduate and post graduate degree.  The ethnicity variable is constructed from a composite of six dummy variables for head of households broken into head of households one and two.  The result is one variable for each where from one to six: Native American, Asian/Pacific Islander, Black/African American, Hispanic/Latino, White/Caucasian, and Other.  For our purposes head of household #2 is ignored.
	Approximately 2.7 times as many households choose to own their homes compared to renters.  As well we see that the majority of households, more than all other categories combined, live in singe family detached houses (See Appendix).  Behind single family houses, large apartment complexes were the most likely dwelling types chosen.  Notably, apartments in general, were more commonly rented than owned as compared to the opposite for each other dwelling type.
	With respect to respondent education attainment, it can be noted that the percentages of each category (see appendix) do differ from that of what can be expected.  It is entirely likely that this is an example of the survey effect on selection of respondents, i.e. that individuals with higher education attainment are more likely to respond to mailed surveys.  Comparing to a cursory internet search for example, more respondents hold graduate degrees and bachelor’s degrees, and less high school diplomas and below than that percentage constructed for the state of California (PPIC).  It is also of minor interest to note the seventy-nine respondents who claim to live in mobile homes and hold graduate degrees.  While that combination of characteristics is plausible enough without further examination, it does bring into question the honesty of respondent’s self-reported information.  But, by constructing a variable equal to the number of housemates over the age of 65 and tabulating it against just mobile homes within the dwelling type variable, we note that the majority of respondents state that 1346 seniors live in mobile homes compared to 643 mobile homes without senior citizens, which is a considerably different trend than homes largely without seniors in the other dwelling type categories particularly detached houses, bearing in mind that this is relatively and the majority of seniors recorded in the data do not live in mobile homes. This may suggests that seniors are utilizing mobile homes as retirement homes, possibly within retirement communities and that would help to explain the minor perceived discrepancy in the education variable.  It is also commonly held that seniors may be more likely to respond to surveys, much like voting, and this would suggest why there are more respondents in mobile homes than in every other category of dwelling aside from home ownership and small complex ownership.  It can be noted from the RASS survey that, in fact, mobile homes had the highest response rate (RASS).

Lastly, one of our variables, actually two, are count variables that account for the number of children under the age of five and between six and eighteen respectively.  This variable was constructed with the intention of finding whether larger structures, in general, such as houses and townhouses, are chosen more often by individuals requiring more room or who are exhibiting more permanent nesting behavior, as in choosing to purchase a home with the intention of residing there for a long period of time and becoming well established.

% latex table generated in R 3.1.3 by xtable 1.7-4 package
% Fri Mar 27 15:08:48 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrr}
  \hline
 & Mobile & SFDetached & SFAttached & SmApartment & LgApartment \\ 
  \hline
FALSEWt & 371 & 5694 & 544 & 430 & 951 \\ 
  FALSEAfAm &  24 & 754 & 121 & 174 & 382 \\ 
  FALSEAsian &   1 & 231 &  48 &  52 & 113 \\ 
  FALSEMulti &   6 &  87 &  14 &  12 &  27 \\ 
  FALSENativeAm &   7 &  35 &   9 &   7 &  15 \\ 
  FALSEOther &   2 &  59 &   8 &  13 &  29 \\ 
  FALSEPacific &   1 &  22 &   1 &   2 &  10 \\ 
  TRUEAfAm &   3 &   8 &  10 &   5 &   8 \\ 
  TRUEAsian &   0 &   5 &   0 &   0 &   1 \\ 
  TRUEMulti &   1 &  10 &   2 &   4 &   4 \\ 
  TRUENativeAm &   2 &  17 &   3 &   6 &   9 \\ 
  TRUEOther &   6 &  41 &  12 &  16 &  24 \\ 
  TRUEPacific &   0 &   2 &   1 &   1 &   0 \\ 
  TRUEWt &  97 & 730 & 105 & 184 & 332 \\ 
   \hline
\end{tabular}
\caption{Count of Observations by Race and Structure Type} 
\label{tab:RaceVStruct}
\end{table}
% latex table generated in R 3.1.3 by xtable 1.7-4 package
% Fri Mar 27 15:08:48 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrr}
  \hline
 & Mobile & SFDetached & SFAttached & SmApartment & LgApartment \\ 
  \hline
NE &  47 & 1173 & 218 & 326 & 470 \\ 
  MidWest &  92 & 2080 & 162 & 145 & 323 \\ 
  South & 245 & 2685 & 257 & 226 & 603 \\ 
  West & 137 & 1757 & 241 & 209 & 509 \\ 
   \hline
\end{tabular}
\caption{Count of Observations by Region and Structure Type} 
\label{tab:RegionVStruct}
\end{table}
\begin{figure}
\begin{center}
\caption{Annual kWh by Rent/Own and Race}
\label{fig:kWhbyOwnRace}
\includegraphics{DraftEdwardsWoods-005}
\end{center}
\end{figure}

@@

% latex table generated in R 3.1.3 by xtable 1.7-4 package
% Fri Mar 27 15:08:54 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrr}
  \hline
 & FALSE & TRUE \\ 
  \hline
FALSEWt & 7606 & 384 \\ 
  FALSEAfAm & 1367 &  88 \\ 
  FALSEAsian & 424 &  21 \\ 
  FALSEMulti & 133 &  13 \\ 
  FALSENativeAm &  68 &   5 \\ 
  FALSEOther & 102 &   9 \\ 
  FALSEPacific &  30 &   6 \\ 
  TRUEAfAm &  31 &   3 \\ 
  TRUEAsian &   4 &   2 \\ 
  TRUEMulti &  19 &   2 \\ 
  TRUENativeAm &  36 &   1 \\ 
  TRUEOther &  88 &  11 \\ 
  TRUEPacific &   4 &   0 \\ 
  TRUEWt & 1330 & 118 \\ 
   \hline
\end{tabular}
\caption{EnergyStar Wall AC by Race and Ethnicity} 
\label{tab:EnergyStarWall}
\end{table}

% latex table generated in R 3.1.3 by xtable 1.7-4 package
% Fri Mar 27 15:08:54 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrr}
  \hline
 & Rural & Urban \\ 
  \hline
FALSEWt & 1937 & 6053 \\ 
  FALSEAfAm & 192 & 1263 \\ 
  FALSEAsian &  14 & 431 \\ 
  FALSEMulti &  28 & 118 \\ 
  FALSENativeAm &  25 &  48 \\ 
  FALSEOther &  12 &  99 \\ 
  FALSEPacific &   4 &  32 \\ 
  TRUEAfAm &   6 &  28 \\ 
  TRUEAsian &   0 &   6 \\ 
  TRUEMulti &   1 &  20 \\ 
  TRUENativeAm &   3 &  34 \\ 
  TRUEOther &   5 &  94 \\ 
  TRUEPacific &   2 &   2 \\ 
  TRUEWt & 137 & 1311 \\ 
   \hline
\end{tabular}
\caption{Race by Urban/Rural} 
\label{tab:UrbRural}
\end{table}

% latex table generated in R 3.1.3 by xtable 1.7-4 package
% Fri Mar 27 15:08:54 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrrrrr}
  \hline
 & NG & LPG & Oil & Kerosene & Elec & Wood & Solar & Other \\ 
  \hline
FALSEWt & 4077 & 315 & 361 &   3 & 3190 &  11 &  12 &   7 \\ 
  FALSEAfAm & 755 &  17 &  35 &   0 & 640 &   0 &   2 &   0 \\ 
  FALSEAsian & 312 &   7 &  12 &   0 & 109 &   0 &   0 &   2 \\ 
  FALSEMulti &  85 &   5 &   3 &   0 &  53 &   0 &   0 &   0 \\ 
  FALSENativeAm &  34 &   2 &   1 &   0 &  36 &   0 &   0 &   0 \\ 
  FALSEOther &  57 &   3 &   6 &   0 &  44 &   0 &   0 &   0 \\ 
  FALSEPacific &  15 &   0 &   2 &   0 &  17 &   0 &   2 &   0 \\ 
  TRUEAfAm &  20 &   0 &   1 &   0 &  13 &   0 &   0 &   0 \\ 
  TRUEAsian &   5 &   0 &   0 &   0 &   1 &   0 &   0 &   0 \\ 
  TRUEMulti &  12 &   0 &   1 &   0 &   8 &   0 &   0 &   0 \\ 
  TRUENativeAm &  29 &   0 &   0 &   0 &   8 &   0 &   0 &   0 \\ 
  TRUEOther &  62 &   1 &   5 &   0 &  30 &   0 &   0 &   0 \\ 
  TRUEPacific &   1 &   1 &   0 &   0 &   2 &   0 &   0 &   0 \\ 
  TRUEWt & 830 &  33 &  26 &   0 & 552 &   0 &   1 &   0 \\ 
   \hline
\end{tabular}
\caption{Water Service by Race and Ethnicity} 
\label{tab:Water}
\end{table}
% latex table generated in R 3.1.3 by xtable 1.7-4 package
% Fri Mar 27 15:08:54 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrrrrrr}
  \hline
 & NG & LPG & Oil & Kerosene & Elec & Wood & Solar & District & Other \\ 
  \hline
FALSEWt & 3987 & 400 & 642 &  40 & 2515 & 245 &   1 &  11 &  19 \\ 
  FALSEAfAm & 674 &  29 &  60 &   6 & 640 &  10 &   0 &   5 &   0 \\ 
  FALSEAsian & 249 &   1 &  21 &   0 & 122 &   1 &   0 &   2 &   0 \\ 
  FALSEMulti &  80 &   6 &   7 &   0 &  41 &   7 &   0 &   0 &   1 \\ 
  FALSENativeAm &  34 &   3 &   1 &   0 &  33 &   2 &   0 &   0 &   0 \\ 
  FALSEOther &  59 &   1 &   9 &   0 &  36 &   3 &   0 &   0 &   0 \\ 
  FALSEPacific &  16 &   0 &   2 &   0 &   5 &   1 &   0 &   0 &   0 \\ 
  TRUEAfAm &  21 &   0 &   1 &   1 &   9 &   0 &   0 &   0 &   0 \\ 
  TRUEAsian &   4 &   0 &   0 &   0 &   1 &   0 &   0 &   0 &   0 \\ 
  TRUEMulti &  11 &   0 &   4 &   0 &   4 &   1 &   0 &   0 &   0 \\ 
  TRUENativeAm &  26 &   1 &   2 &   0 &   7 &   0 &   0 &   0 &   0 \\ 
  TRUEOther &  53 &   0 &   8 &   1 &  32 &   0 &   0 &   2 &   0 \\ 
  TRUEPacific &   1 &   0 &   0 &   0 &   2 &   0 &   0 &   0 &   0 \\ 
  TRUEWt & 604 &  25 &  51 &   2 & 540 &  18 &   0 &   3 &   1 \\ 
   \hline
\end{tabular}
\caption{Heating Fuel by Race and Ethnicity} 
\label{tab:HeatFuel}
\end{table}
% latex table generated in R 3.1.3 by xtable 1.7-4 package
% Fri Mar 27 15:08:54 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrr}
  \hline
 & VColdCold & HotDryMixedDry & HotHumid & MixedHumid & Marine \\ 
  \hline
FALSEWt & 3118 & 850 & 1216 & 2382 & 424 \\ 
  FALSEAfAm & 299 & 131 & 383 & 611 &  31 \\ 
  FALSEAsian &  95 & 128 &  60 &  77 &  85 \\ 
  FALSEMulti &  51 &  27 &  13 &  40 &  15 \\ 
  FALSENativeAm &  23 &  10 &   7 &  28 &   5 \\ 
  FALSEOther &  29 &  16 &  24 &  37 &   5 \\ 
  FALSEPacific &   4 &   6 &  13 &   4 &   9 \\ 
  TRUEAfAm &  16 &   5 &   4 &   9 &   0 \\ 
  TRUEAsian &   2 &   2 &   1 &   0 &   1 \\ 
  TRUEMulti &  12 &   6 &   1 &   0 &   2 \\ 
  TRUENativeAm &   9 &  14 &   1 &   8 &   5 \\ 
  TRUEOther &  35 &  19 &  10 &  28 &   7 \\ 
  TRUEPacific &   2 &   0 &   2 &   0 &   0 \\ 
  TRUEWt & 237 & 481 & 406 & 237 &  87 \\ 
   \hline
\end{tabular}
\caption{Climate by Race and Ethnicity} 
\label{tab:Climate}
\end{table}
\begin{figure}
\begin{center}
\caption{Age of Structure by Rent/Own and Race/Ethnicity}
\label{fig:AgebyOwnRace}
\includegraphics{DraftEdwardsWoods-013}
\end{center}
\end{figure}

@@

% latex table generated in R 3.1.3 by xtable 1.7-4 package
% Fri Mar 27 15:08:56 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrrrr}
  \hline
 & Never & ThreeDay & TwoDay & OneDay & FewWeek & OneWeek & LessWeek \\ 
  \hline
FALSEWt &  67 & 452 & 1814 & 3303 & 1825 & 254 & 275 \\ 
  FALSEAfAm &  11 & 156 & 351 & 341 & 448 &  80 &  68 \\ 
  FALSEAsian &   4 &  63 & 111 & 148 &  91 &  13 &  15 \\ 
  FALSEMulti &   2 &  14 &  45 &  40 &  36 &   7 &   2 \\ 
  FALSENativeAm &   0 &   7 &  22 &  27 &  11 &   3 &   3 \\ 
  FALSEOther &   2 &  10 &  25 &  21 &  43 &   3 &   7 \\ 
  FALSEPacific &   0 &   3 &   9 &  10 &  11 &   0 &   3 \\ 
  TRUEAfAm &   1 &   4 &   7 &  13 &   9 &   0 &   0 \\ 
  TRUEAsian &   0 &   0 &   1 &   3 &   2 &   0 &   0 \\ 
  TRUEMulti &   0 &   2 &   1 &  11 &   5 &   2 &   0 \\ 
  TRUENativeAm &   0 &   3 &  12 &  15 &   4 &   2 &   1 \\ 
  TRUEOther &   0 &  20 &  28 &  31 &  14 &   3 &   3 \\ 
  TRUEPacific &   0 &   3 &   0 &   1 &   0 &   0 &   0 \\ 
  TRUEWt &  22 & 208 & 453 & 435 & 226 &  42 &  62 \\ 
   \hline
\end{tabular}
\caption{Weekly Meals Cooked by Race and Ethnicity} 
\label{tab:Cooking}
\end{table}
\begin{figure}
\begin{center}
\caption{Daytime Temp and Race/Ethnicity (Winter)}
\label{fig:TempHomeRace}
\includegraphics{DraftEdwardsWoods-015}
\end{center}
\end{figure}

@@

% latex table generated in R 3.1.3 by xtable 1.7-4 package
% Fri Mar 27 15:09:57 2015
